---
title: "DATA 607 - Week 9 Assignment"
author: "N Nedd"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: HPSTR
    highlight: github
---

# Setup of packages
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
if("jsonlite" %in% rownames(installed.packages()) == FALSE) {install.packages("jsonlite")}
library(jsonlite)
if("dplyr" %in% rownames(installed.packages()) == FALSE) {install.packages("dplyr")}
library(dplyr)
if("stringr" %in% rownames(installed.packages()) == FALSE) {install.packages("stringr")}
library(stringr)
if("ggplot2" %in% rownames(installed.packages()) == FALSE) {install.packages("ggplot2")}
library(ggplot2)
if("rtimes" %in% rownames(installed.packages()) == FALSE) {install.packages("rtimes")}
library(rtimes)
```

#Read in names of NY Times best selling lists from API
```{r readin-names, eval=TRUE}
NYT_url <- "https://api.nytimes.com/svc/books/v3/lists/names.json?"
API_Key <- "fdfd28b541314f5793618f60cefbd084"
namesRaw <- fromJSON(paste(NYT_url, "api-key=",API_Key, sep=""))
namesData <- namesRaw$results
head(namesData)

```

##Isolate fiction lists

```{r filter-fiction, eval = TRUE}
fictionNames <- filter(namesData, str_detect(namesData$display_name, "Fiction"))


```


#Read in Current Bestseller fiction lists
```{r readin, eval=TRUE}
NYT_url <- "https://api.nytimes.com/svc/books/v3/lists.json?"
API_Key <- "fdfd28b541314f5793618f60cefbd084"
allData <- data.frame()
for(i in 1:nrow(fictionNames)){
  pageData <- fromJSON(paste(NYT_url, "&api-key=",API_Key, "&list=",fictionNames$list_name_encoded[i],sep= ""), simplifyDataFrame = TRUE)
  allData <- rbind(allData, pageData$results)
}
head(allData)
```


##Extract Book Details
```{r book-details, eval=TRUE}
detailsData <- data.frame()
for(i in 1:nrow(allData)){
detailsData <- rbind(detailsData,as.data.frame(allData$book_details[i]))
}

head(detailsData)
```

##Combine Book Details with Book Data and select interesting columns

```{r combine-data, eval=TRUE}
bookData <- cbind(allData, detailsData)
analyseData <- select(bookData, title, author, publisher, rank, weeks_on_list)
head(analyseData)
```


#Analyse Data

##Highest number of weeks on list (top 5)

```{r highest-weeks, eval=TRUE}
analyseData_weeks <- arrange(analyseData, desc(weeks_on_list))
top_5 <- analyseData_weeks[1:5,]

ggplot(top_5, aes(title,weeks_on_list)) + geom_bar(stat="identity") +theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```

**There are duplicate books in the table indicating a repeat on the best seller list**



#Using rtimes api

A look at recent news items about best selling fiction.  The as_search function searches the New York Times articles.

```{r article-search, eval=TRUE}
best_articles <- as_search(q="best+seller+fiction",begin_date='20170101',end_date='20170331',key=API_Key)
best_articles$meta
best_articles$data[1:3]
```


